SemanticPaint

### 2015-12-02 cv3d_seminar/paper.tex
related works finished

  Capturing your own enviornment has never been easier. SemanticPaint can register your surroundings which, after undergoing a low-level 3D reconstruction, can be semanticly segmented in an interactive way. Not only it works in real time but also requires no pretraining. Adding new object categories on the fly is facilitated by online model updates. The user is provided with instantenous feedback and can re-label any object to correct errors. SemanticPaint makes capturing customized enviornment models with object classes particular to the user's interest easy and efficient.

  The pipeline starts with capturing the enviornment as a stream of noisy RGBD images and combining them into a updated 3D model in an online fashion. The user can choose which objects to label and can do so by ``touching'' a small part of an object or encircling one with his hand and uttering the label. It is recognized by a standard speech recognition system. The label and the information about the affected data points are further passed to a Streaming Random Forest classifier which constantly learns and labels all visible voxels. To further improve classification results a spatially dense labeling is produced by an efficient mean-field inference algorithm. One of the biggest strength of SemanticPaint is the efficiency of each part of the pipeline, which translates to real time performance. Algorithms used in the pipeline were adapted to work on volumentric data in the TSDF format directly in order to avoding the costly conversions to mesh or point-cloud formats. To allow this, the Voxel Oriented Patch features --- a new type of a descriminative feature describing the voxel space --- has been designed. 
  The contributions can be summarized as follows: 3D semantic modeling system, Streaming Random Forest, efficient Mean-Field inference, Voxel Oriented Patch features.

  Numerous applications are possible: (1) building large scale datasets of 3D objects or whole scenes for use in large-scale computer vision systems (2) using the dense semantic labeling of 3D enviornments in robot navigation or to aid people with impaird sight and (3) map enviornments for use in augmanted reality scenerios or games.

  The rest of the paper is organised as follows: Section 2. describes the related work, section 3 details internal data handling, section 4 describes the efficient mean-field inference algorithm, section 5 outlint the Streaming Random Forest classifiers.....

@@

%   Outline:
%   1) what has generally been done and use cases

    Capturing the geometry of the surrounding world has been a long standing problem. We have managed to reconstruct digital heritage and construct world-scale 3D models with remarkable quality using offline processing from multiple images. Since low-cost RGBD sensors and powerful GPUs have become available, whch enabled online 3D scanning, augmented reality or using 3D enviornment models for navigation purposes.

%   2) scene understanding

      There are a number of approaches to scene understanding. Some of them work on 2D RGB images, other reconstruct geometry from multiple RGB images but still use only 2D data for classification purposes and back-project the results into the 3D model. Yet other approaches focus on geometric data exclusively. Since RGBD sensors are available there has been a growing interest in working with RGBD data, point clouds or voxel representations. There has been some work on segmenting 3D scenes and meshes, detect objects in small scenes or replace them with synthetic models.

      There has been some work on semantic segmentation of 3D meshes; These methods consider mostly noise-free meshes, do not work in real time and use geometric features only. Some work has been done on matching scan data with databases of synthetic 3D models. It would allow to replace noisy point clouds with detailed models to improve reconstruction quality and decrease memory requirements by exploiting repetetiveness. Usually a model is split into parts individually matched against an offline-built database. It is too slow for real-time usage.

      There exists an online SLAM system that recognizes objects and perform online model updatres, but it supports only a single object class and relatively small scenes. What's appealing is that it does semantic recognition and reconstruction.

      There are no approaches that can handle an outdoor setting. Most of the work focused on image classification. No system works in real-time nor does online model updates. They also do not use ful 3d information, or do so in a global optimization setting which is slow.

  \cite{Monofusion} enables 3D reconstruction of small since using a single off-the-shelf RGB camera. It uses a sparse tracking method to first estimate the camera's pose and then select key frames and relative to them secondary frames from which 3D stereo reconstruction is perfomed. Results achieved are similar to KinectFusion with the only limitation being low precision of reconstruction of textureless surfaces.

  \cite{ChangeDetection} is a first step towards online simultaneous registration and segmentation. Using RGBD images, the framework constructs a model of the enviornment and updates it each time a new frame comes in. When a significant change in the model is detected, the resulting model is split into a static and a dynamic part, where the latter is assumed to have moved in space. The movement is detected by comparing the expected and observed intensity values at each voxel. The system is online, but is far from real time with 0.7 to 2s processing time per frame.

  \cite{mesh}

  \cite{VCRF} uses a Voxel-based CRF for simultaneous segmentation and reconstruction. Each voxel contains information about visibility and occlusion as well as group membership. The first two are used to to improve reconstruction by mitigating depth-map noise. The visibility values are constrained by that each ray from the camera can hit only one visible vortex. The group membership information encodes priors given by bounding boxes of detected objects. A graph-cut algorithm is used for inference, which is performed globally. No computational performance was reported.

@@

\section{Pipeline}
\section{Mean-Field Inference}
\section{Streaming Random Forest}
\section{Voxel-Oriented Patch Features}
\section{Qualitative Results}
\section{Quantitative Results}
\section{Discussion}
\section{Concolusions}

@@

	%Each item starts with a \bibitem{reference} command and the details thereafter.
	\bibitem{HOP96} % Transaction paper
	J.~Hagenauer, E.~Offer, and L.~Papke. Iterative decoding of binary block
	and convolutional codes. {\em IEEE Trans. Inform. Theory},
	vol.~42, no.~2, pp.~429–-445, Mar. 1996.
	\bibitem{MJH06} % Conference paper
	T.~Mayer, H.~Jenkac, and J.~Hagenauer. Turbo base-station cooperation for intercell interference cancellation. {\em IEEE Int. Conf. Commun. (ICC)}, Istanbul, Turkey, pp.~356--361, June 2006.

	\bibitem{Proakis} % Book
	J.~G.~Proakis. {\em Digital Communications}. McGraw-Hill Book Co.,
	New York, USA, 3rd edition, 1995.

	\bibitem{talk} % Web document
	F.~R.~Kschischang. Giving a talk: Guidelines for the Preparation and Presentation of Technical Seminars.
	\url{http://www.comm.toronto.edu/frank/guide/guide.pdf}.

@@

>>>>

  Capturing your own environment has never been easier. SemanticPaint can register your surroundings which, after undergoing a low-level 3D reconstruction, can be semantically segmented in an interactive way. Not only it works in real time but also requires no pretraining. Adding new object categories on the fly is facilitated by online model updates. The user is provided with instantaneous feedback and can re-label any object to correct errors. SemanticPaint makes capturing customized environment models with object classes particular to the user's interest easy and efficient.

  The pipeline starts with capturing the environment as a stream of noisy RGBD images and combining them into a updated 3D model in an online fashion. The user can choose which objects to label and can do so by ``touching'' a small part of an object or encircling one with his hand and uttering the label. It is recognized by a standard speech recognition system. The label and the information about the affected data points are further passed to a Streaming Random Forest classifier which constantly learns and labels all visible voxels. To further improve classification results a spatially dense labeling is produced by an efficient mean-field inference algorithm. One of the biggest strength of SemanticPaint is the efficiency of each part of the pipeline, which translates to real time performance. Algorithms used in the pipeline were adapted to work on volumetric data in the TSDF format directly in order to avoiding the costly conversions to mesh or point-cloud formats. To allow this, the Voxel Oriented Patch features --- a new type of a discriminative feature describing the voxel space --- has been designed. 
  The contributions can be summarized as follows: 3D semantic modeling system, Streaming Random Forest, efficient Mean-Field inference, Voxel Oriented Patch features.

  Numerous applications are possible: (1) building large scale datasets of 3D objects or whole scenes for use in large-scale computer vision systems (2) using the dense semantic labeling of 3D environments in robot navigation or to aid people with impaired sight and (3) map environments for use in augmented reality scenarios or games.

  The rest of the paper is organized as follows: Section 2. describes the related work, section 3 details internal data handling, section 4 describes the efficient mean-field inference algorithm, section 5 outline the Streaming Random Forest classifiers.....

@@

  \textbf{Acquisition and Reconstruction.} Capturing the geometry of the surrounding world has been a long standing problem \cite{old}. An offline processing of multiple images allowed to reconstruct digital heritage and construct world-scale 3D models with remarkable quality \cite{heritage}. The inception of low-cost RGBD sensors and powerful GPUs enabled online 3D scanning, augmented reality or using 3D environment models for navigation purposes \cite{fusion}. \cite{Monofusion} enables 3D reconstruction of small scenes using a single off-the-shelf RGB camera. It uses a sparse tracking method to first estimate the camera's pose and then select key frames and relative to them secondary frames, from which 3D stereo reconstruction is performed. The achieved results are similar to KinectFusion with the only limitation being that the precision of texture-less surfaces' reconstruction is somewhat lacking.

  \noindent
  \textbf{Scene Understanding.} Object recognition, detection and segmentation has been done with 2D RGB images, RGBD data, point clouds and volumetric representations. \cite{VCRF} uses a Voxel-based CRF for simultaneous reconstruction and segmentation. Each voxel contains information about visibility and occlusion as well as group membership. The first two are used to to improve reconstruction by mitigating depth-map noise. The visibility values are constrained by that each ray from the camera can hit only one visible vortex. The group membership information encodes priors given by bounding boxes of detected objects. A graph-cut algorithm is used for global inference. The whole scene has to be registered beforehand, since any change in the CRF's structure would require restarting the inference algorithm. No computational performance was reported. \cite{ChangeDetection} is a first step towards online simultaneous registration and segmentation. Using RGBD images, the framework constructs a model of the environment and updates it each time a new frame comes in. When a significant change in the model is detected, the resulting model is split into a static and a dynamic part, where the latter is assumed to have moved in space. The movement is detected by comparing the expected and observed intensity values at each voxel. The system is online, but is far from real time with 0.7 to 2s processing time per frame. \cite{mesh} shows that converting to another data representation can help to improve segmentation accuracy and inference speed. TSDF model is used to reconstruct a 3D scene from a sequence of RGBD images. The volumetric representation is triangulated and a 3D mesh is recovered. Next, visual features are computed directly on images and projected into the 3D model, while geometric features are computed on the mesh directly. Segmentation is done via a CRF. The approach is tested on the augmented KITTI and NYU datasets for indoor and outdoor scene segmentation where it delivers state-of-the-art results.

@@

% \section{Pipeline}
% \section{Mean-Field Inference}
% \section{Streaming Random Forest}
% \section{Voxel-Oriented Patch Features}
% \section{Qualitative Results}
% \section{Quantitative Results}
% \section{Discussion}
% \section{Conclusions}

@@

  \bibitem{old}
  ROBERTS , L. G. 1963. Machine perception of three-dimensional solids. Ph.D. thesis, Massachusetts Institute of Technology.

@@

  \bibitem{heritage}
  LEVOY , M., PULLI , K., CURLESS , B., RUSINKIEWICZ , S., KOLLER , D., EREIRA , L., GINZTON , M., ANDERSON , S., DAVIS , J., G NSBERG , J., ET AL . 2000. The digital Michelangelo project: 3D scanning of large statues. In Proc. SIGGRAPH. ACM.

  \bibitem{fusion}
  NEWCOMBE , R. A., IZADI , S., HILLIGES , O., MOLYNEAUX , D., KIM , D., DAVISON , A. J., KOHLI , P., SHOTTON , J., HODGES , S., AND FITZGIB-BON , A. 2011. KinectFusion: Real-time dense surface mapping and tracking. In Proc. ISMAR.
